### 2011-11-26 AffineLieAlgebras/Thesis/1.tex
+tr

Соотношение (\ref{eq:111}) и асимптотика функций  and the asymptotics of the branching functions can be used
to prove the finite reducibility theorem \cite{kac1988modular}.
It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
only finite number of branching coefficients have nonzero values.

>>>>

Если рассмотреть соотношение (\ref{eq:111}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}. Она утверждает, что для конформного вложения  $\af\longrightarrow\mathfrak{g}$ лишь конечное число коэффициентов ветвления отлично от нуля.
